% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,a4paper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xcolor}

\newcommand{\updateinfo}[1][\today]{\par\vfill\hfill{\scriptsize\color{gray}Last updated on #1}}


\usepackage{fancyhdr}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage[none]{hyphenat}

% Set your name here
\def\name{Sandeep Rath}



\fancyhf{}
\cfoot{ Last updated: \today }
% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdfkeywords = {economics, statistics, mathematics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	body={6.5in,10in},
	left=1.0in,
	top=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
\end{list}
}

\newcommand{\cvdoublecolumn}[2]{%
  \cvitem[0.75em]{}{%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}%
    }%
}

% usage: \cvreference{name}{address line 1}{address line 2}{address line 3}{address line 4}{e-mail address}{phone number}
% Everything but the name is optional
% If \addresssymbol, \emailsymbol or \phonesymbol are specified, they will be used.
% (Per default, \addresssymbol isn't specified, the other two are specified.)
% If you don't like the symbols, remove them from the following code, including the tilde ~ (space).

\newcommand{\cvreference}[7]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}}


\begin{document}

	% Place name at left
	{\huge \name}

	% Alternatively, print name centered and bold:
	%\centerline{\huge \bf \name}

	\vspace{0.25in}

	\begin{minipage}{0.45\linewidth}
		\href{http://www.unc.edu/}{
			Kenan Flagler Business School\\
			University of North Carolina} \\
		McColl 4705 \\
		CB\# 3490 \\
		Chapel Hill, NC 27599
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\begin{tabular}{ll}
			Phone: & (919) 962-3818 \\
			Fax: &  (919) 962-6949 \\
			Email: & \href{mailto:sandeep@unc.edu}{\tt sandeep@unc.edu} \\
			Homepage: & \href{https://rathsandeep.github.io/}{\tt rathsandeep.github.io}\\
		\end{tabular}
	\end{minipage}


	%\section*{Personal}

	%\begin{itemize}
	%\item Born on September 29, 1895.
	%\item United States Citizen.
	%\end{itemize}


	\section*{\textbf{Education}}

	\begin{itemize}
		\item \textbf{UCLA Anderson School of Management, Los Angeles}
		\begin{itemize}
			\item Ph.D. Management,  June, 2016.
			\item \emph{Dissertation Title}: Resource Planning Models for Healthcare Organizations.
			\item \emph{Dissertation committee}: Kumar Rajaram (chair), Felipe Caro, Uday Karmarkar, {Aman Mahajan}.
		\end{itemize}
		\item \textbf{Indian Institute of Technology, Kharagpur}
		\begin{itemize}
			\item M.Tech. Instrumentation Engineering, 2006.
			\item B.Tech. Electrical Engineering, 2006.
			\begin{itemize}
			\item[\textendash] Minor, Electronics and Telecommunication Engineering.
		\end{itemize}
		\end{itemize}




	\end{itemize}


	\section*{\textbf{Professional Experience}}

	\begin{itemize}
		\item \textbf{Kenan-Flagler Business School, University of North Carolina at Chapel Hill}

		\begin{itemize}
			\item Assistant Professor, 2016--present.
		\end{itemize}
		\item \textbf{UCLA Anderson School of Management, Los Angeles}

		\begin{itemize}
			\item Teaching Assistant, Executive MBA Program, Fall 2016.
			\item Teaching Assistant, Fully Employed MBA Program, Fall Quarters of 2012--2016.
		\end{itemize}

		\item \textbf{Indian School of Business, Hyderabad}

		\begin{itemize}
			\item Research Associate, 2010--2011.
		\end{itemize}


		\item \textbf{Schlumberger Ltd., Pune}
		\begin{itemize}
			\item Business Analyst,  2008--2009
			\item Manufacturing Engineer, 2007--2008.
		\end{itemize}
		\item \textbf{ITC Ltd., Chennai}

		\begin{itemize}
			\item Assistant Manager 2006--2007.
		\end{itemize}

	\end{itemize}

	\section*{\textbf{Honors}}

	\begin{itemize}
		\item Nominated for Weatherspoon Undergraduate Teaching Award, 2023
		\item POMS CHOM Research-in-Practice Showcase Presentation, 2022
		\item Finalist, INFORMS Innovative Application in Analytics Award, 2022
		\item UCLA Dissertation Year Fellowship, 2015--2016.
		\item UCLA Anderson Doctoral Fellowship, 2011--2015.
		\item Fellowship for Post Graduate Studies, Government of India,  2005--2006.
		\item National Talent Search Examination Scholarship, Government of India, 1999--2005.
	\end{itemize}


	\section*{\textbf{Publications}}

	\subsection*{Peer-Reviewed Journal Articles}
	
	\emph{* indicates healthcare practitioner or physician collaborator}

	\begin{itemize}
			\item Deshpande V., Mundru N., \textbf{Rath, S.}, *Knowles M., *Rowe D., *Wood B.C. (2023),  Data-Driven Surgical Tray Optimization to Improve Operating Room Efficiency \emph{Operations Research} (35 pages)
		\begin{itemize}
			\item[\textendash] {Finalist}, INFORMS Innovative Application in Analytics Award (2022)
			\item[\textendash] Selected for POMS College of Healthcare Operations Management Research-in-Practice Showcase Presentations (2022)
			\item[\textendash] Media Coverage: Collaborating to Cut Hospital Costs\\ (https://www.kenan-flagler.unc.edu/research/collaborating-to-cut-hospital-costs/)
		\end{itemize}
		
		\item \textbf{Rath, S.}, \& Rajaram, K. (2022). Staff Planning for Hospitals with Implicit Cost Estimation and Stochastic Optimization. \emph{Production and Operations Management}, 31(3), 1271-1289.
		\begin{itemize}
			\item[\textendash] Media Coverage: A Scheduling Tool that Considers Employee Preferences \emph{UCLA Anderson Review} (Nov 2021)
		\end{itemize}
		\item \textbf{Rath, S.}, Rajaram, K., \&* Mahajan, A. (2017). Integrated Anesthesiologist and Room Scheduling for Surgeries: Methodology and Application. \emph{Operations Research}, 65(6), 1460-1478. \mbox{(18 pages)}.
		\item Wood, B.C., Konchan, S., Gay, S., \textbf{Rath, S.}, Deshpande, V. and Knowles, M., (2021). Data analysis of plastic surgery instrument trays yields significant cost savings and efficiency gains. \emph{Annals of Plastic Surgery}, 86(6S), pp.S635-S639.
		\item Knowles, M., Gay, S.S., Konchan, S.K., Mendes, R., \textbf{Rath, S.}, Deshpande, V., Farber, M.A. and Wood, B.C., (2021). Data analysis of vascular surgery instrument trays yielded large cost and efficiency savings. \emph{Journal of Vascular Surgery}, 73(6), pp.2144-2153.
		\item Deo, S., Rajaram, K., \textbf{Rath, S.}, Karmarkar, U. S., \& *Goetz, M. B. (2015). Planning for HIV Screening, Testing, and Care at the Veterans Health Administration. \emph{Operations Research}, 63(2), 287-304 (18 pages).
	\end{itemize}
\subsection*{Articles Under Review/Revision}
\begin{itemize}
\item Celik U., \textbf{Rath, S.}, Kesavan S., Staats B., Does Physician Choice of When to Perform EHR Tasks Influence Total EHR Workload? (35 pages) \emph{Under $2^{nd}$ round review at M\&SOM}
\item \textbf{Rath, S.} Rajaram K., *Hudson, M.E., *Mahajan A., Multi-location, Dynamic Staff Planning for a Healthcare System: Methodology and Application (37 pages) \emph{Under Review at Operations Research}
	

\end{itemize}

\subsection*{Working Papers}
\begin{itemize}
	\item \textbf{Rath, S.}, Swaminathan, J.M., *Coleman C., Collaborative Care for Mental and Physical Health (34 pages) \emph{Under preparation for submission}
	
\end{itemize}

\subsection*{Work in Progress}

\begin{itemize}
	\item Celik U., \textbf{Rath, S.}, Staats B., Kesavan S.,  Reducing Appointment Delays: The Impact of 
	Standardized EHR Usage on Physician Timeliness (\emph{Data collection complete, analysis in progress})
	\item \textbf{Rath, S.}, *Lim M., Data-Driven Surgical Block Release Planning (\emph{Data collection complete, analysis in progress})
	\item \textbf{Rath, S.}, Kesavan S.,   Staats B., Appointment Scheduling with Offline Discretionary Work (\emph{Data collection complete, analysis in progress})
\end{itemize}
\subsection*{Other Published Articles}

\begin{itemize}
	\item Rajaram, K., \& \textbf{Rath, S.} (2017). Managing the Operating Room Suite at UCLA Ronald Reagan Medical Center. \emph{Impact}, 3(2), 31-35.
\end{itemize}


%	\subsection*{Other Published Articles}
%
%	\begin{itemize}
%		\item Rajaram, K., \& \textbf{Rath, S.} (2017). Managing the Operating Room Suite at UCLA Ronald Reagan Medical Center. Impact, 3(2), 31-35.
%	\end{itemize}


	\section*{\textbf{Teaching Record}}

	\begin{itemize}
		\item\textbf{ Undergraduate Program, Kenan-Flagler Business School, University of North
			Carolina}
		\begin{itemize}
			\item BUSI 403: Operations Management, Undergraduate Core, \emph{Spring 2017-2023}, Average Instructor Rating: 4.67/5

%			\begin{itemize}
%%				\item \emph{Spring 2019}: In progress
%%				\item \emph{Spring 2018}: Instructor Rating 4.58/5, 4.71/5
%%				\item \emph{Spring 2017}: Instructor Rating 4.79/5, 4.69/5
%
%			\end{itemize}


			\item BUSI 532H: Healthcare and Service Operations Management, Undergraduate Elective, \emph{Spring 2018-2023}, Average Instructor Rating: 4.69/5
			\begin{itemize}
				\item[\textendash] Course listed as Service Operations Management between 2018-2022
			\end{itemize}
%			\begin{itemize}
%				\item \emph{Spring 2019}: In progress
%				\item \emph{Spring 2018}: Instructor Rating 4.82/5
%			\end{itemize}
		\end{itemize}

	\end{itemize}


	\section*{\textbf{Peer-Reviewed Conference Presentations}}
	\begin{itemize}

		\item \emph{Data-Driven Surgical Tray Optimization to Improve Operating Room Efficiency}
		\begin{itemize}
			\item POMS College of Healthcare Operations Management Research-in-Practice Showcase Presentation (2022)
		\end{itemize}

		\item \emph{Collaborative Care for Mental and Physical Health}
			\begin{itemize}
				\item Manufacturing \& Service Operations Management Conference, 2022.
			\item Manufacturing \& Service Operations Management Conference, 2021.
		\end{itemize}
		\item \emph{Staff Planning for Hospitals with Cost Estimation and
			Optimization}
		\begin{itemize}
			\item Manufacturing \& Service Operations Management Conference, 2019.
			\item Manufacturing \& Service Operations Management Conference, 2018.

		\end{itemize}
	\end{itemize}
	\section*{\textbf{Invited Conference Presentations}}
	\begin{itemize}
			\item \emph{Data-Driven Approach to the Surgical Block Release Decision}
		\begin{itemize}
			\item INFORMS Annual Meeting (Phoenix 2023) 
		\end{itemize}
		\item \emph{Multilocation, Dynamic Staff Planning for a Healthcare System: Methodology and Application}
		\begin{itemize}
			\item POMS Annual Meeting (Orlando 2023) 
		\end{itemize}
		\item \emph{Data-driven Workforce Planning For Healthcare Organizations}
		\begin{itemize}
			\item INFORMS Annual Meeting (Indianapolis 2022) 
		\end{itemize}
		
		\item \emph{Data-Driven Surgical Tray Optimization to Improve Operating Room Efficiency}
		\begin{itemize}
			\item POMS Annual Meeting (Online, 2022)
		\end{itemize}
		\item \emph{Appointment Scheduling with Off-line Discretionary Work}
		\begin{itemize}
			\item POMS Annual Conference (Online, 2022), INFORMS Annual Meeting  (Anaheim 2021).
		\end{itemize}
		\item \emph{Collaborative Care for Mental and Physical Health}
		\begin{itemize}
			\item POMS Annual Conference (Online, 2022), POMS Annual Conference (Online, 2021), INFORMS Annual Meeting (Seattle, 2019), INFORMS Healthcare (Boston, 2019), INFORMS Annual Meeting (Phoenix 2018).

		\end{itemize}
		\item \emph{Staff Planning For Anesthesiologists}
		\begin{itemize}
			%\item INFORMS Annual Meeting, Phoenix 2018 (presented by co-author).
			\item INFORMS Annual Meeting (Seattle, 2019), INFORMS Healthcare (Boston, 2019), INFORMS Annual Meeting (Houston, 2017), INFORMS Annual Meeting (Nashville, 2016)

		\end{itemize}
		\item \emph{Integrated Staff and Room Scheduling for Surgeries}
		\begin{itemize}
			\item INFORMS Healthcare (Rotterdam, 2017), INFORMS Annual Meeting (Nashville, 2016), INFORMS Annual Meeting (Philadelphia, 2015), INFORMS Healthcare, (Nashville, 2015)
		\end{itemize}
		\item \emph{Planning for HIV Screening, Testing, and Care}
		\begin{itemize}
			\item INFORMS Annual Meeting, San Francisco, 2014.
		\end{itemize}
	\end{itemize}
	\section*{\textbf{Other Invited Presentations}}


	\begin{itemize}

		\item University of Kansas School of Business (scheduled, April 2024)
		\item Workshop in Management Science, San Pedro de Atacama, Chile (scheduled, December 2023)
		\item Carlson School of Management, University of Minnesota (scheduled, November 2023)
		\item Johns Hopkins Carey Business School (scheduled, November, 2023)
		\item Robert H. Smith School of Business, University of Maryland (scheduled, November 2023)
		\item UNC Kenan-Flagler Center for the Business of Health Faculty Research Share Session (scheduled, October 2023)
		\item Midwest Healthcare Workshop, Geis College of Business, UIUC, 2023
		\item Department of Statistics and Operations Research, UNC, 2023
		\item Sloan School of Management, MIT, 2023
		\item Carroll School of Management, Boston College, 2023 
		\item NC State Doing Good with OM/OR Workshop, 2022
		\item Kelley School of Business, Indiana University, Consortium Friday Seminar Series (online), 2021
		\item UNC Business of Healthcare Convocation, Chapel Hill, 2019
		\item Kenan-Flagler Business School, University of North Carolina, Chapel-Hill, 2015.
		\item Communication, Networks and Systems Seminar, University of Southern California, 2015.
		\item Southern California OR/OM Day, Los Angeles, 2015.
		\item DOTM Colloquium Series, UCLA Anderson, 2015.
	
			

\end{itemize}


	\section*{\textbf{Professional Service}}
	\subsection*{To the Discipline}
	\begin{itemize}
		\item \textbf{Reviewer}
		\begin{itemize}

			\item California Management Review, IISE Transactions,  Management Science, Manufacturing \& Service Operations Management, Naval Research Logistics, Operations Research, Production and Operations Management %(h-index: 209), Number of papers reviewed: 1


		\end{itemize}
		\item \textbf{Judge}
		\begin{itemize}
				\item INFORMS Health Application Society Best Student Paper Competition, 2023
			\item INFORMS Public Sector OR Best Paper Competition, 2022
			\item MSOM Conference Healthcare SIG, 2021, 2022, 2023
			\item Pierskalla Best Paper Award, 2020
			\item POMS College of Healthcare Operations Management, Best Paper Competition, 2017, 2020, 2021, 2022, 2023
		\end{itemize}
		\item \textbf{Conference Track Chair}
	\begin{itemize}
		\item POMS Annual Meeting, Orlando (2023)
	\end{itemize}
		\item \textbf{Conference Session Chair}
		\begin{itemize}
			\item  INFORMS Annual Meetings: Phoenix (\emph{scheduled}, 2023), Anaheim (2021), Seattle (2019), Phoenix (2018, co-chair with Jayashankar  Swaminathan), Houston (2017), Philadelphia (2015)
			\item INFORMS Healthcare: Toronto (\emph{scheduled}, 2023), Boston (2019), Nashville (2015)
			\end{itemize}

	\end{itemize}
	\subsection*{Within UNC Chapel Hill}
	\begin{itemize}
		\item Organizing Committee Member, UNC Healthcare Operations Workshop, 2019
		\item Operations Area Faculty Seminar Series, Chair, 2017-2019.
		\item Organizing Committee Member, Manufacturing \& Service Operations Management Conference, 2017.
	\end{itemize}
\section*{\textbf{References}}
\emph{Available on request}
	\updateinfo[\today]

\end{document}
